Exploiting the Social Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-26 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Little extension and comments

 \section{IEC Human-centered framework}
\label{sec:graph}
The general goal of this research is to develop a human-centered \cite{gasson2003human} framework
for interactive evolutionary computation (IEC) in order to increase
participation and also to minimize the amount of evaluations needed for the
evolutionary process in given IEC application. We deliberately use the 
more general
term Human instead of User, because humans are not always playing the role of
users in software engineering sense, they could just be interacting 
naturally with their environment and with out knowing they are implicitly
evaluating a possible solution. In other cases the evaluation could be done
by the natural interactions of a group of humans in a collaborative fashion
or not. For instance the IEC algorithm could by trying to optimize 
the design of an exit sign in an airport, then the quality of this sign could be
determined by the average time it takes a sample of people to 
find the exit. In this example there could be certain collaboration
between users if they are not traveling alone, of course this is only one of
the considerations designers could make.

@@

>>>>

 \section{IEC Human-centered framework}
\label{sec:graph}
The general goal of this research is to develop a human-centered \cite{gasson2003human} framework
for interactive evolutionary computation (IEC) in order to increase
participation and also to minimize the amount of evaluations needed for the
evolutionary process in given IEC application. We deliberately use the 
more general
term Human instead of User, because humans are not always playing the role of
users in software engineering sense, they could just be interacting 
naturally with their environment and with out knowing they are implicitly
evaluating a possible solution. In other cases the evaluation could be done
by the natural interactions of a group of humans in a collaborative fashion
or not. For instance the IEC algorithm could be trying to optimize 
the design of an exit sign in an airport, then the quality of this sign could be
determined by the average time it takes a sample of people to 
find the exit. In this example there could be certain collaboration
between users if they are not traveling alone, but of course this is only one of
the considerations designers could make.

@@

These components will be described in detail next.
% Besides, add something about the innovation in this paper, for
% instance, explaining that the data model is extended to a graph here
% - JJ
